Summer 2025 ToDo

### 2025-05-29 Relations/Paper/Implications.tex
Tables updated to be clearer

\begin{table}[h!]
    \centering
    {\setlength{\arrayrulewidth}{1.5pt}  % Set horizontal rule thickness
    \begin{tabular}{|>{\columncolor{gray!30}}l!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}c|c|}
        \hline
        \rowcolor{gray!30} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$} & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$} & \multicolumn{2}{c|}{$\SN$} \\
        \hline
        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
        \hline
    \end{tabular}}
    \caption{Local implications}
\end{table}
\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \begin{tabular}{|>{\columncolor{gray!30}}l|c|c|c|c|c|}
        \hline
        \rowcolor{gray!30}     & $\gWM$         & $\gWN$         & $\gSM$             & $\gSMandWN$        & $\gSN$ \\
        \hline
        $\gUNto$ &  CE-\ref{CE:2}, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} , CE-\ref{CE:9}      & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[1] , CE-\ref{CE:9}          & $\gCR$, $\gSN$      & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ , CE-\ref{CE:9}    & $\gCR$, CE-\ref{CE:7}    & $\gCR$\footnotemark[2] , CE-\ref{CE:9} & $\gCR$, $\gSN$    & $\gCR$\footnotemark[2] , $\gSN$ \\
        \hline
        $\gCR$   & $\gCR$, CE-\ref{CE:9}     & $\gCR$, CE-\ref{CE:7}     & $\gCR$, CE-\ref{CE:9}        & $\gCR$, $\gSN$      & $\gCR$ , $\gSN$ \\
        \hline

    \end{tabular}
    \caption{Global implications}
\end{table}
\footnotetext[1]{This implication also requires $\gWCR$.}
\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
$\SN \to \WN$ or $\SM \to \WM$.}
\renewcommand*{\thefootnote}{\arabic{footnote}}

>>>>

\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\WN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\SN$} \\
        \Xhline{1.5pt}
        $\UNto$ & CE-\ref{CE:4} & CE-\ref{CE:12} & CE-\ref{CE:4} & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$\footnotemark[1] & CE-\ref{CE:4} & $\CR$\footnotemark[1] & $\SN$ \\
        \hline
        $\NP$ & CE-\ref{CE:10} & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[1] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\MP$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$\footnotemark[2] & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$\footnotemark[2] & $\SN$ \\
        \hline
        $\CR$ & $\CR$ & CE-\ref{CE:9} & $\CR$ & CE-\ref{CE:7} & $\CR$ & CE-\ref{CE:9} & $\CR$ & $\SN$ & $\CR$ & $\SN$ \\
        \hline
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Local implications}
\end{table}

\vspace{-1cm}
% \\[-0.5cm]
\begin{table}[h!]
    \centering
    \renewcommand\arraystretch{1.2}
    \begin{tabular}{!{\vrule width 1.5pt}
        >{\columncolor{gray!30}}l
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c
        !{\vrule width 1.5pt}c|c!{\vrule width 1.5pt}}
        \Xhline{1.5pt}
        \rowcolor{gray!30} 
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSM$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSMandWN$}
        & \multicolumn{2}{c!{\vrule width 1.5pt}}{$\gSN$} \\
        \Xhline{1.5pt}
        $\gUNto$ & CE-\ref{CE:2} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gNP$ & CE-\ref{CE:3} & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[1] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gMP$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$\footnotemark[2] & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$\footnotemark[2] & $\gSN$ \\
        \hline
        $\gCR$ & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & CE-\ref{CE:7} & $\gCR$ & CE-\ref{CE:9} & $\gCR$ & $\gSN$ & $\gCR$ & $\gSN$ \\
        \Xhline{1.5pt}
    \end{tabular}
    \caption{Global implications}
\end{table}
\footnotetext[1]{This implication also requires $\gWCR$.}
\footnotetext[2]{This implication also requires either $\gWCR$ or the classical property required to go from 
$\SN \to \WN$ or $\SM \to \WM$.}
\renewcommand*{\thefootnote}{\arabic{footnote}}
